### 2023-11-15 Scripts/Manuscript/manuscript.Rmd
added all of the figure and table cross-references to the project, and changed the spacing in tables to be smaller.

  Enter author note here. Caspar?

@@

# creates a reference list for all used R packages and the installed R version (does not include Rstudio)
r_refs("r-references.bib")

@@

The publicly available datasets of the replication attempt were accessed through their OSF page and loaded into Rstudio [@Posit2023RStudio] with R version 4.2.2 [@R2021R]. Using the replication protocols, codebooks, and analysis scripts from each replication set as a guide, the variables associated with each measure were extracted into their own data frame containing the data from all studies in one replication set. These pieces of information formed the replication datasets in the analysis.

@@

## Measures {#sec:measures}

@@

\renewcommand{\arraystretch}{0.5}
```{r QMPCodingInfoTable}
QMP_info_dataframe <-data.frame(Category = c("Definition", "", "", "Operationalisation", "", "", "", "Selection/Creation", "", "", "Quantification", "Modification", "", "", "", "", ""),
           'N Questions' = c("1", "", "", "5", "", "", "", "4", "", "", "4", "6", "", "", "", "", ""),
           'Example Question' = c("A psychological/sociological definition",
            "is given to the name of the measured",
            "variable within the paper.", 
            "The administration format (pen-and-",
            "paper/computer) and environment (in",
            "public/in a lab) are described (Note:",
            "both should be present for a true rating).", 
            "The source of the scale is provided",
            "(in case the scale was newly developed",
            "this should be clearly stated).", 
            "The number of items are described.", 
            "Any format changes are mentioned",
            "(paper-and-pencil <–> computer), if no",
            "changes were made to the format, and",
            "this was mentioned then code as No",
            "modification. If it is not clear, then code",
            "as False."))

@@

```
\renewcommand{\arraystretch}{1}

@@

```{=tex}
\begin{align*}
& Level 1: alpha_{ij} = \beta_{0j} + e_{ij} \qquad\qquad\quad e_{ij} \sim N(0, \sigma_{e}^{2}) \\
& Level 2: \beta_{0j} = \gamma_{00} + u_{0j} \qquad\qquad\qquad u_{0j} \sim N(0, \sigma_{u0}^{2}) \\
& Mixed: alpha_{ij} = \gamma_{00} + u_{0j} + e_{ij}
\end{align*}
```
```{r Hypothesis 2 Model, include = FALSE}
# intercept only model to check the within and between group variance.
H2_test_result_alpha <- lmer(formula = alpha ~ 1 + (1|g), data = data_h2)

@@

$$ICC = \frac{u_{0j}}{(e_{ij} + u_{0j})}$$

@@

$$f(replicated_{i}) = \beta_{0} + \beta_{1} alpha_{i}$$

@@

$$f(.) = log\frac{p_{replicated}}{1 - p_{replicated}}$$

@@

The reported analyses were primarily based on the revised set of QMP data. The results using the original QMP data are mentioned when the results led to different conclusions. The analysis code for both the original and revised QMP data are available in R script on the OSF page of this thesis: <https://osf.io/9r8yt/>.

@@

$$g(.) = (0, 1) \mapsto \mathbb{R}$$

@@

$$g(QMP\_ratio_{i}) = \beta_{0} + \beta_{1} replication_{i}$$

@@

$$g(QMP\_ratio_{i}) = \beta_{0} + \beta_{1} replicated_{i}$$

@@

$$g(QMP\_ratio\_replication_{i}) = \beta_{0} + \beta_{1} QMP\_ratio\_original_{i}$$

@@

The mean sample size within the replications was `r apa_num(mean(coded_data_replications$N, na.rm = TRUE), digits = 0)` participants (IQR = `r apa_num(IQR(coded_data_replications$N, na.rm = TRUE), digits = 0)`). In the original articles the mean sample size was `r apa_num(mean(coded_data_original_shortened$N, na.rm = TRUE), digits = 0)` (IQR = `r apa_num(IQR(coded_data_original_shortened$N, na.rm = TRUE), digits = 0)`). In total, support was found for hypothesized effects of `r apa_num(table(coded_data_replications$hypothesis_support)["Yes"], digits = 0)` of the `r apa_num(nrow(coded_data_replications), digits = 0)` measures. Proportions of replication success per Many Labs project can be found in Table XXX.

```{r Replication Ratio Table}
# construct the replication ratio table to be printed
replication_ratio_table <- data.frame("Many Labs Version" = c("1", "2", "3", "5", "Total"),
                                      "N Total" = c(table(coded_data_replications$many_labs_version), nrow(coded_data_replications)), 
                                      "N Replicated" = c(table(coded_data_replications$many_labs_version, coded_data_replications$hypothesis_support)[, "Yes"], table(coded_data_replications$hypothesis_support)["Yes"]))

@@

Figure XXX depicts the type of measure (single-item, multiple item, or not a scale), if for the measure reliability was reported or not, and what type of reliability coefficient was reported. Reliabilities were only assessed for multiple item measures, which were approximately equal between replication and original (`r apa_num(table(coded_data_replications$N_items)["multiple item measure"])` and `r apa_num(table(coded_data_original_shortened$N_items)["multiple item measure"])`, respectively). Looking at the multiple item measures, `r apa_num(sum(table(coded_data_replications$N_items, coded_data_replications$reliability_type)["multiple item measure", - c(1, 3)]), numerals = FALSE)` in the replication protocols and `r apa_num(sum(table(coded_data_original_shortened$N_items, coded_data_original_shortened$reliability_type)["multiple item measure", - c(1, 3, 4)]), numerals = FALSE)` in the original articles reported a reliability coefficient. The most commonly reported reliability coefficient was Cronbach's alpha, which accounted for `r apa_num(sum(table(coded_data_replications$N_items, coded_data_replications$reliability_type)["multiple item measure", "alpha"]), numerals = FALSE)` out of `r apa_num(sum(table(coded_data_replications$N_items, coded_data_replications$reliability_type)["multiple item measure", - c(1, 3)]), numerals = FALSE)` reported reliabilities in the replication protocols, and `r apa_num(sum(table(coded_data_original_shortened$N_items, coded_data_original_shortened$reliability_type)["multiple item measure", "alpha"]), numerals = FALSE)` out of `r apa_num(sum(table(coded_data_original_shortened$N_items, coded_data_original_shortened$reliability_type)["multiple item measure", - c(1, 3, 4)]), numerals = FALSE)` in the original articles.

![Figure 1. Reliability reporting flow diagram](../../SupplementaryMaterials/reliability_reporting_flow_diagram.png)

@@

The average Cronbach's alpha coefficient across replication sets was `r apa_num(mean(data_h3_multiple$alpha), digits = 3)` with a standard deviation of `r apa_num(mean(data_h3_multiple$omega, na.rm = TRUE), digits = 3)`, for omega the mean was `r apa_num(sd(data_h3_multiple$alpha), digits = 3)` with a standard deviation of `r apa_num(sd(data_h3_multiple$omega, na.rm = TRUE), digits = 3)`. Figure XXX shows the distributions of the Cronbach's alpha coefficients for each replication set separated by successful and unsuccessful replication.

```{r Plot 23 Alpha Code}
# plot for alpha
ggplot(plot_23_data_alpha, aes(x = alpha, y = g)) +
  geom_boxplot(outlier.shape = NA) +
  geom_hline(yintercept = 6.5, color = "red", size = 1) +
  geom_point(alpha = 0.1) +
  theme_minimal() +
  theme(legend.position = "none", plot.margin = unit(c(1, 6.5, 1, 1), 
                                                     "lines")) +
  annotation_custom(grob = textGrob(label = "Not Replicated", hjust = 0),
    ymin = 7, ymax = 7, xmin = 1.08, xmax = 1.08) +
  annotation_custom(grob = textGrob(label = "Replicated", hjust = 0),
    ymin = 6, ymax = 6, xmin = 1.08, xmax = 1.08) +
  coord_cartesian(xlim = c(0, 1), clip = "off") +
  ylab("") +
  xlab("Cronbach's alpha")

@@

```{r Plot 23 Omega Code, include = FALSE, eval = FALSE}
# plot for omega
ggplot(plot_23_data_omega, aes(x = alpha, y = g)) +
  geom_boxplot(outlier.shape = NA) +
  geom_hline(yintercept = 6.5, color = "red", size = 1) +
  geom_point(alpha = 0.1) +
  theme_minimal() +
  theme(legend.position = "none", plot.margin = unit(c(1, 6.5, 1, 1), 
                                                     "lines")) +
  annotation_custom(grob = textGrob(label = "Not Replicated", hjust = 0),
    ymin = 6, ymax = 6, xmin = 1.08, xmax = 1.08) +
  annotation_custom(grob = textGrob(label = "Replicated", hjust = 0),
    ymin = 5, ymax = 5, xmin = 1.08, xmax = 1.08) +
  coord_cartesian(xlim = c(0, 1), clip = "off") +
  ylab("") +
  xlab("Omega")

The between-group (across different replication set) variance and within-group (lab locations within a replication set) variance in the Cronbach's alpha coefficient were assessed using a multilevel model as specified in Formulas XXX, XXX, & XXX. The between-group and within-group variance for Cronbach's alpha were approximately `r apa_num(between_group_variance_alpha, digits = 3)` and `r apa_num(within_group_variance_alpha, digits = 3)` respectively. The resulting ICC, obtained using formula XXX, was approximately `r apa_num(ICC_alpha, digits = 3)`. This suggests that variance was larger between replication sets than within. The same analysis for omega coefficients even showed a relatively larger degree of between group variance (between-group variance `r apa_num(within_group_variance_omega, digits = 3)`, within-group variance `r apa_num(between_group_variance_omega, digits = 3)`, ICC = `r apa_num(ICC_omega, digits = 3)`). Both results are in line with hypothesis 2, although caution in interpreting this result is advised due to the small sample size and the lack of an available inferential test.

The relationship between reliability and replication success was primarily tested via logistic regression, with replication success as the dependent variable. Further sensitivity analyses were performed using multilevel logistic models, with each measure as an overarching group wherein its reliability at each lab location is nested. The results of the logistic and multilevel logistic models are shown in Table XXX for both Cronbach's alpha and omega reliability coefficients.

```{r Replicability and Reliability Test Table}
# creating the dtaframe for the table
H3_table_dataframe <- rbind(H3_test_result_main_alpha$table, H3_test_result_int_sensitivity_alpha$table, H3_test_result_main_omega$table, H3_test_result_int_sensitivity_omega$table, H3_test_result_slp_sensitivity_omega$table)

@@

Cronbach's alpha and omega did not significantly relate to replication success in the main logistic regression model (Cronbachs alpha: `r H3_test_result_main_alpha$full_result$alpha`; omega: `r H3_test_result_main_omega$full_result$omega`), nor in any of the multilevel sensitivity analyses models (see Table XXX). This is contradictory to the expectation in hypothesis 3. However, the results from these analyses should be evaluated with caution, given the small sample number of measures used to estimate these models.

@@

The counts of the QMP ratio obtained for each QMP type (see Table XXX) are shown across the top layer of Figure XXX for both replication protocols and original articles. The overall number of counts for the QMP ratios of the QMP modification type were lower compared to the others, because only `r apa_num(table(coded_data_replications$mod_check)["True"])` out of `r apa_num(length(coded_data_replications$mod_check))` measures in replications, and only `r apa_num(table(coded_data_original_shortened$mod_check)["True"], numerals = FALSE)` measures used in original studies were modified. The bottom layer of Figure XXX shows the overlayed distributions of the total QMP ratios from the replication protocols and original studies, with dots indicating each datapoint, and the line indicating the mean for either distribution.

```{r Plot 456 Code}
# plot for alpha
### ratio (REV) Original and Rep
Plot_456_1 <- ggplot(plot_456_data[plot_456_data$QMP_type != "Total",], 
       aes(x = QMP_ratio, fill = RepOrg)) + 
  geom_bar(position = "dodge", stat = "bin", bins = 10) +
  facet_grid(~QMP_type) +
  theme_minimal() +
  theme(plot.title = element_text(face = "bold")) +
  scale_fill_manual(values=c("brown", "blue4")) +
  theme(legend.position = "none") +
  ylab("Count") +
  xlab("QMP Ratio") +
  ggtitle("QMP Ratio's Per QMP Type Grouped by Original and Replication") +
  scale_x_continuous(labels = c("0", "0.25", "0.5", "0.75", "1"))

@@

```{r Plot 46 Initial Data Code, include = FALSE, eval = FALSE, error = FALSE}
# Initial
ggplot(plot_46_data, aes(QMP_ratio, QMP_Rep_ratio)) + 
  geom_point() +
  geom_jitter(width = 0.05, height = 0.05) +
  stat_smooth(method="lm") + 
  theme_bw() +
  theme(strip.text.y = element_text(size = 7), strip.background = element_rect(
    color = "black", fill = "white", size = 1, linetype = "solid"
  )) +
  xlab("QMP Ratio (Original)") + ylab("QMP Ratio (Replication)") +
  scale_x_continuous(labels = c("0", "0.25", "0.5", "0.75", "1")) + 
  facet_grid(vars(QMP_Rep_type), vars(QMP_type))

@@

```{r Plot 46 Revised Data Code, error = FALSE}
# Revised
ggplot(plot_46_data_rev, aes(QMP_ratio, QMP_Rep_ratio)) + 
  geom_point() +
  geom_jitter(width = 0.05, height = 0.05) +
  stat_smooth(method="lm") + 
  theme_bw() +
  theme(strip.text.y = element_text(size = 7), strip.background = element_rect(
    color = "black", fill = "white", size = 1, linetype = "solid"
  )) +
  xlab("QMP Ratio (Original)") + ylab("QMP Ratio (Replication)") +
  scale_x_continuous(labels = c("0", "0.25", "0.5", "0.75", "1")) + 
  facet_grid(vars(QMP_Rep_type), vars(QMP_type))

@@

Planned exploratory analyses were preformed to expand on the test for hypothesis 6. The relationships between original article QMP ratios and replication protocol QMP ratios were investigated for each QMP type separately. Table XXX shows the results from these tests with the revised protocol QMP coding, while Table XXX shows the results for the QMP ratios obtained via the initial protocol. There were few significant relations and even fewer that are consistent between both coding protocols. The relations that are consistent are those between original article definition QMPs with replication selection and total QMPs, original article selection QMPs with replication total QMPs, and finally original article quantification QMPs with replication selection QMPs. All of these relations were positive across both coding protocols, illustrating that a greater QMP ratio of the specified type in an original article is associated with an increase in QMP ratio for the specific QMP type, or total QMP ratio in the replication protocol.

```{r H6 Exploratory Associations Revised Table}
# creating the dataframe for the table
H6_table_dataframe_l_REV <- rbind(Results_H6_between_REV$def_def, Results_H6_between_REV$def_op,
  Results_H6_between_REV$def_sel, Results_H6_between_REV$def_quant, Results_H6_between_REV$def_mod, 
  Results_H6_between_REV$op_def, Results_H6_between_REV$op_op, Results_H6_between_REV$op_sel, 
  Results_H6_between_REV$op_quant, Results_H6_between_REV$op_mod, Results_H6_between_REV$sel_def, 
  Results_H6_between_REV$sel_op, Results_H6_between_REV$sel_sel, Results_H6_between_REV$sel_quant, 
  Results_H6_between_REV$sel_mod)

@@

```{r H6 Exploratory Associations Initial Table}
# creating the dataframe for the table
H6_table_dataframe_l <- rbind(Results_H6_between$def_def, Results_H6_between$def_op,
  Results_H6_between$def_sel, Results_H6_between$def_quant, Results_H6_between$def_mod, 
  Results_H6_between$op_def, Results_H6_between$op_op, Results_H6_between$op_sel, 
  Results_H6_between$op_quant, Results_H6_between$op_mod, Results_H6_between$sel_def, 
  Results_H6_between$sel_op, Results_H6_between$sel_sel, Results_H6_between$sel_quant, 
  Results_H6_between$sel_mod)

@@

Figure XXX visually illustrates the relations of QMP ratios from different QMP types between replication protocols and original articles further.

The unidimensionality of the measures used in the Many Labs projects was assessed through factor analyses, and evaluated based on the criteria discussed in section XXX. Suitable data for factor analyses was available for nineteen measures. These measures were the same as those shown in Figure XXX, with the addition of one more measure from [@cacioppo1983effects]. A composite score based on the measurement responses was used for sixteen of the nineteen measures to form a single variable in the analyses, and were thus regarded as intended to be unidimensional. The number of dimensions for the remaining three were unclear. Sufficient fit of the unidimensional model was found for six out of the nineteen evaluated measures. However, as shown in Table XXX the unidimensional model did not hold for any measure data based on the parallel analysis test alone. Only the RMSEA $< .08$ criteria suggested evidence for single factor structures.

>>>>

  Enter author note here. Caspar/Jelte/Marjan?

@@

# creates a reference list for all used R packages and the installed R version (does not automatically include Rstudio)
r_refs("r-references.bib")

# manually retrieving the Rstudio version

@@

The publicly available datasets of the replication attempt were accessed through their OSF page and loaded into Rstudio XXXRSTUDIOREFERENCEHEREXXX. with R version 4.2.2 XXXRREFERENCEHEREXXX. Using the replication protocols, codebooks, and analysis scripts from each replication set as a guide, the variables associated with each measure were extracted into their own data frame containing the data from all studies in one replication set. These pieces of information formed the replication datasets in the analysis.

@@

## Measures

@@

\renewcommand{\arraystretch}{0.7}

```{r QMPCodingInfoTable}
QMP_info_dataframe <-data.frame(Category = c("Definition", "", "", "Operationalisation", "", "", "", "Selection/Creation", "", "", "Quantification", "Modification", "", "", "", "", ""),
           'N Questions' = c("1", "", "", "5", "", "", "", "4", "", "", "4", "6", "", "", "", "", ""),
           'Example Question' = c("A psychological/sociological definition",
            "is given to the name of the measured",
            "variable within the paper.", 
            "The administration format (pen-and-",
            "paper/computer) and environment (in",
            "public/in a lab) are described (Note:",
            "both should be present for a true rating).", 
            "The source of the scale is provided",
            "(in case the scale was newly developed",
            "this should be clearly stated).", 
            "The number of items are described.", 
            "Any format changes are mentioned",
            "(paper-and-pencil <–> computer), if no",
            "changes were made to the format, and",
            "this was mentioned then code as No",
            "modification. If it is not clear, then code",
            "as False."))

@@

@@

```{=tex}
\begin{align}
& Level 1: alpha_{ij} = \beta_{0j} + e_{ij} \qquad\qquad\quad e_{ij} \sim N(0, \sigma_{e}^{2}) (\#eq:level1H2) \\
& Level 2: \beta_{0j} = \gamma_{00} + u_{0j} \qquad\qquad\qquad u_{0j} \sim N(0, \sigma_{u0}^{2}) (\#eq:level2H2) \\
& Mixed: alpha_{ij} = \gamma_{00} + u_{0j} + e_{ij} (\#eq:mixedH2)
\end{align}
```
```{r Hypothesis 2 Model, include = FALSE}
# intercept only model to check the within and between group variance.
H2_test_result_alpha <- lmer(formula = alpha ~ 1 + (1|g), data = data_h2)

@@

```{=tex}
\begin{equation}
ICC = \frac{u_{0j}}{(e_{ij} + u_{0j})} (\#eq:ICC)
\end{equation}
```

@@

```{=tex}
\begin{equation}
f(replicated_{i}) = \beta_{0} + \beta_{1} alpha_{i} (\#eq:H3Main)
\end{equation}
```

@@

```{=tex}
\begin{equation}
f(.) = log\frac{p_{replicated}}{1 - p_{replicated}} (\#eq:LogitLink)
\end{equation}
```

@@

The reported analyses were primarily based on the revised set of QMP data. The results using the original QMP data are mentioned when the results led to different conclusions. The analysis code for both the original and revised QMP data are available in the R script on both the OSF page (<https://osf.io/9r8yt/>) and github page (<https://github.com/CasGoos/measurement_and_replication.git>) of this article.

@@

```{=tex}
\begin{equation}
g(.) = (0, 1) \mapsto \mathbb{R} (\#eq:BetaLink)
\end{equation}
```

@@

```{=tex}
\begin{equation}
g(QMP\_ratio_{i}) = \beta_{0} + \beta_{1} replication_{i} (\#eq:H4Main)
\end{equation}
```

@@

```{=tex}
\begin{equation}
g(QMP\_ratio_{i}) = \beta_{0} + \beta_{1} replicated_{i} (\#eq:H5Main)
\end{equation}
```

@@

```{=tex}
\begin{equation}
g(QMP\_ratio\_replication_{i}) = \beta_{0} + \beta_{1} QMP\_ratio\_original_{i} (\#eq:H6Main)
\end{equation}
```

@@

The mean sample size within the replications was `r apa_num(mean(coded_data_replications$N, na.rm = TRUE), digits = 0)` participants (IQR = `r apa_num(IQR(coded_data_replications$N, na.rm = TRUE), digits = 0)`). In the original articles the mean sample size was `r apa_num(mean(coded_data_original_shortened$N, na.rm = TRUE), digits = 0)` (IQR = `r apa_num(IQR(coded_data_original_shortened$N, na.rm = TRUE), digits = 0)`). In total, support was found for hypothesized effects of `r apa_num(table(coded_data_replications$hypothesis_support)["Yes"], digits = 0)` of the `r apa_num(nrow(coded_data_replications), digits = 0)` measures. Proportions of replication success per Many Labs project can be found in Table \@ref(tab:ReplicationRatioTable).

```{r ReplicationRatioTable}
# construct the replication ratio table to be printed
replication_ratio_table <- data.frame("Many Labs Version" = c("1", "2", "3", "5", "Total"),
                                      "N Total" = c(table(coded_data_replications$many_labs_version), nrow(coded_data_replications)), 
                                      "N Replicated" = c(table(coded_data_replications$many_labs_version, coded_data_replications$hypothesis_support)[, "Yes"], table(coded_data_replications$hypothesis_support)["Yes"]))

@@

Figure \@ref(fig:ReliabilityReportingFlowDiagram) depicts the type of measure (single-item, multiple item, or not a scale), if for the measure reliability was reported or not, and what type of reliability coefficient was reported. Reliabilities were only assessed for multiple item measures, which were approximately equal between replication and original (`r apa_num(table(coded_data_replications$N_items)["multiple item measure"])` and `r apa_num(table(coded_data_original_shortened$N_items)["multiple item measure"])`, respectively). Looking at the multiple item measures, `r apa_num(sum(table(coded_data_replications$N_items, coded_data_replications$reliability_type)["multiple item measure", - c(1, 3)]), numerals = FALSE)` in the replication protocols and `r apa_num(sum(table(coded_data_original_shortened$N_items, coded_data_original_shortened$reliability_type)["multiple item measure", - c(1, 3, 4)]), numerals = FALSE)` in the original articles reported a reliability coefficient. The most commonly reported reliability coefficient was Cronbach's alpha, which accounted for `r apa_num(sum(table(coded_data_replications$N_items, coded_data_replications$reliability_type)["multiple item measure", "alpha"]), numerals = FALSE)` out of `r apa_num(sum(table(coded_data_replications$N_items, coded_data_replications$reliability_type)["multiple item measure", - c(1, 3)]), numerals = FALSE)` reported reliabilities in the replication protocols, and `r apa_num(sum(table(coded_data_original_shortened$N_items, coded_data_original_shortened$reliability_type)["multiple item measure", "alpha"]), numerals = FALSE)` out of `r apa_num(sum(table(coded_data_original_shortened$N_items, coded_data_original_shortened$reliability_type)["multiple item measure", - c(1, 3, 4)]), numerals = FALSE)` in the original articles.

```{r ReliabilityReportingFlowDiagram, fig.cap = "Reliability reporting flow diagram."}
knitr::include_graphics(path = "../../SupplementaryMaterials/reliability_reporting_flow_diagram.png")
```

@@

The average Cronbach's alpha coefficient across replication sets was `r apa_num(mean(data_h3_multiple$alpha), digits = 3)` with a standard deviation of `r apa_num(mean(data_h3_multiple$omega, na.rm = TRUE), digits = 3)`, for omega the mean was `r apa_num(sd(data_h3_multiple$alpha), digits = 3)` with a standard deviation of `r apa_num(sd(data_h3_multiple$omega, na.rm = TRUE), digits = 3)`. Figure \@ref(fig:Plot23AlphaCode) shows the distributions of the Cronbach's alpha coefficients for each replication set separated by successful and unsuccessful replication.

```{r Plot23AlphaCode, fig.cap = "Distributions of calculated Cronbach’s alpha coefficients (> 0) calculated for the responses on a measure at each lab location, across the eighteen distinct measures for which suitable raw data was available to calculate Cronbach’s alpha coefficients from."}
# plot for alpha
ggplot(plot_23_data_alpha, aes(x = alpha, y = g)) +
  geom_boxplot(outlier.shape = NA) +
  geom_hline(yintercept = 6.5, color = "red", size = 1) +
  geom_point(alpha = 0.1) +
  theme_minimal() +
  theme(legend.position = "none", plot.margin = unit(c(1, 6.5, 1, 1), 
                                                     "lines")) +
  annotation_custom(grob = textGrob(label = "Not Replicated", hjust = 0),
    ymin = 7, ymax = 7, xmin = 1.08, xmax = 1.08) +
  annotation_custom(grob = textGrob(label = "Replicated", hjust = 0),
    ymin = 6, ymax = 6, xmin = 1.08, xmax = 1.08) +
  coord_cartesian(xlim = c(0, 1), clip = "off") +
  ylab("") +
  xlab("Cronbach's alpha")

@@

```{r Plot23OmegaCode, include = FALSE, eval = FALSE}
# plot for omega
ggplot(plot_23_data_omega, aes(x = alpha, y = g)) +
  geom_boxplot(outlier.shape = NA) +
  geom_hline(yintercept = 6.5, color = "red", size = 1) +
  geom_point(alpha = 0.1) +
  theme_minimal() +
  theme(legend.position = "none", plot.margin = unit(c(1, 6.5, 1, 1), 
                                                     "lines")) +
  annotation_custom(grob = textGrob(label = "Not Replicated", hjust = 0),
    ymin = 6, ymax = 6, xmin = 1.08, xmax = 1.08) +
  annotation_custom(grob = textGrob(label = "Replicated", hjust = 0),
    ymin = 5, ymax = 5, xmin = 1.08, xmax = 1.08) +
  coord_cartesian(xlim = c(0, 1), clip = "off") +
  ylab("") +
  xlab("Omega")
```

The between-group (across different replication set) variance and within-group (lab locations within a replication set) variance in the Cronbach's alpha coefficient were assessed using a multilevel model as specified in Formulas \@ref(eq:level1H2), \@ref(eq:level2H2), & \@ref(eq:mixedH2) The between-group and within-group variance for Cronbach's alpha were approximately `r apa_num(between_group_variance_alpha, digits = 3)` and `r apa_num(within_group_variance_alpha, digits = 3)` respectively. The resulting ICC, obtained using formula \@ref(eq:ICC), was approximately `r apa_num(ICC_alpha, digits = 3)`. This suggests that variance was larger between replication sets than within. The same analysis for omega coefficients even showed a relatively larger degree of between group variance (between-group variance `r apa_num(within_group_variance_omega, digits = 3)`, within-group variance `r apa_num(between_group_variance_omega, digits = 3)`, ICC = `r apa_num(ICC_omega, digits = 3)`). Both results are in line with hypothesis 2, although caution in interpreting this result is advised due to the small sample size and the lack of an available inferential test.

The relationship between reliability and replication success was primarily tested via logistic regression, with replication success as the dependent variable. Further sensitivity analyses were performed using multilevel logistic models, with each measure as an overarching group wherein its reliability at each lab location is nested. The results of the logistic and multilevel logistic models are shown in Table \@ref(tab:ReplicabilityReliabilityTestTable) for both Cronbach's alpha and omega reliability coefficients.

```{r ReplicabilityReliabilityTestTable}
# creating the dtaframe for the table
H3_table_dataframe <- rbind(H3_test_result_main_alpha$table, H3_test_result_int_sensitivity_alpha$table, H3_test_result_main_omega$table, H3_test_result_int_sensitivity_omega$table, H3_test_result_slp_sensitivity_omega$table)

@@

Cronbach's alpha and omega did not significantly relate to replication success in the main logistic regression model (Cronbachs alpha: `r H3_test_result_main_alpha$full_result$alpha`; omega: `r H3_test_result_main_omega$full_result$omega`), nor in any of the multilevel sensitivity analyses models (see Table \@ref(tab:ReplicabilityReliabilityTestTable)). This is contradictory to the expectation in hypothesis 3. However, the results from these analyses should be evaluated with caution, given the small sample number of measures used to estimate these models.

@@

The counts of the QMP ratio obtained for each QMP type (see Table \@ref(tab:QMPCodingInfoTable)) are shown across the top layer of Figure \@ref(fig:Plot456Code) for both replication protocols and original articles. The overall number of counts for the QMP ratios of the QMP modification type were lower compared to the others, because only `r apa_num(table(coded_data_replications$mod_check)["True"])` out of `r apa_num(length(coded_data_replications$mod_check))` measures in replications, and only `r apa_num(table(coded_data_original_shortened$mod_check)["True"], numerals = FALSE)` measures used in original studies were modified. The bottom layer of Figure \@ref(fig:Plot456Code) shows the overlayed distributions of the total QMP ratios from the replication protocols and original studies, with dots indicating each datapoint, and the line indicating the mean for either distribution.

```{r Plot456Code, fig.cap = "QMP ratio counts for each QMP Type and QMP total ratio distribution grouped by where each was coded from. The top row shows binned counts of QMP ratio’s that were observed for each replication protocol and original article, across the different QMP types. The bottom graph shows the distributions of total QMP ratios for both replication protocols and original articles, with the line indicating the mean QMP ratio. The specific observed values are indicated along the bottom row with dots"}
# plot for alpha
### ratio (REV) Original and Rep
Plot_456_1 <- ggplot(plot_456_data[plot_456_data$QMP_type != "Total",], 
       aes(x = QMP_ratio, fill = RepOrg)) + 
  geom_bar(position = "dodge", stat = "bin", bins = 10) +
  facet_grid(~QMP_type) +
  theme_minimal() +
  theme(plot.title = element_text(face = "bold")) +
  scale_fill_manual(values=c("brown", "blue4")) +
  theme(legend.position = "none") +
  ylab("Count") +
  xlab("QMP Ratio") +
  ggtitle("QMP Ratio's Per QMP Type Grouped by Original and Replication") +
  scale_x_continuous(labels = c("0", "0.25", "0.5", "0.75", "1"))

@@

```{r Plot46InitialDataCode, include = FALSE, eval = FALSE, error = FALSE}
# Initial
ggplot(plot_46_data, aes(QMP_ratio, QMP_Rep_ratio)) + 
  geom_point() +
  geom_jitter(width = 0.05, height = 0.05) +
  stat_smooth(method="lm") + 
  theme_bw() +
  theme(strip.text.y = element_text(size = 7), strip.background = element_rect(
    color = "black", fill = "white", size = 1, linetype = "solid"
  )) +
  xlab("QMP Ratio (Original)") + ylab("QMP Ratio (Replication)") +
  scale_x_continuous(labels = c("0", "0.25", "0.5", "0.75", "1")) + 
  facet_grid(vars(QMP_Rep_type), vars(QMP_type))

@@

```{r Plot46RevisedDataCode, error = FALSE, fig.cap = "Scatterplot of original and replication QMP ratio’s per type with linear regression line. The abbreviations on the axes relate to the QMP categories described in Table 1: Def. is definition, Op. is operationalization, Sel. is selection/creation, Quant. is quantification, and Mod. is modification. The X axis facets across the QMP ratios in the original articles, and the Y axis facets across the QMP ratios in the replication protocols. Each dot in the figure relates to describes the QMP ratio for the types in that graph across an original article and its replication protocol. Note: jitter was applied to these dots in order to show the number of observations at points where multiple dots were present"}
# Revised
ggplot(plot_46_data_rev, aes(QMP_ratio, QMP_Rep_ratio)) + 
  geom_point() +
  geom_jitter(width = 0.05, height = 0.05) +
  stat_smooth(method="lm") + 
  theme_bw() +
  theme(strip.text.y = element_text(size = 7), strip.background = element_rect(
    color = "black", fill = "white", size = 1, linetype = "solid"
  )) +
  xlab("QMP Ratio (Original)") + ylab("QMP Ratio (Replication)") +
  scale_x_continuous(labels = c("0", "0.25", "0.5", "0.75", "1")) + 
  facet_grid(vars(QMP_Rep_type), vars(QMP_type))

@@

Planned exploratory analyses were preformed to expand on the test for hypothesis 6. The relationships between original article QMP ratios and replication protocol QMP ratios were investigated for each QMP type separately. Table \@ref(tab:H6ExploratoryAssociationsRevisedTable) shows the results from these tests with the revised protocol QMP coding, while Table \@ref(tab:H6ExploratoryAssociationsInitialTable) shows the results for the QMP ratios obtained via the initial protocol. There were few significant relations and even fewer that are consistent between both coding protocols. The relations that are consistent are those between original article definition QMPs with replication selection and total QMPs, original article selection QMPs with replication total QMPs, and finally original article quantification QMPs with replication selection QMPs. All of these relations were positive across both coding protocols, illustrating that a greater QMP ratio of the specified type in an original article is associated with an increase in QMP ratio for the specific QMP type, or total QMP ratio in the replication protocol.

```{r H6ExploratoryAssociationsRevisedTable}
# creating the dataframe for the table
H6_table_dataframe_l_REV <- rbind(Results_H6_between_REV$def_def, Results_H6_between_REV$def_op,
  Results_H6_between_REV$def_sel, Results_H6_between_REV$def_quant, Results_H6_between_REV$def_mod, 
  Results_H6_between_REV$op_def, Results_H6_between_REV$op_op, Results_H6_between_REV$op_sel, 
  Results_H6_between_REV$op_quant, Results_H6_between_REV$op_mod, Results_H6_between_REV$sel_def, 
  Results_H6_between_REV$sel_op, Results_H6_between_REV$sel_sel, Results_H6_between_REV$sel_quant, 
  Results_H6_between_REV$sel_mod)

@@

```{r H6ExploratoryAssociationsInitialTable}
# creating the dataframe for the table
H6_table_dataframe_l <- rbind(Results_H6_between$def_def, Results_H6_between$def_op,
  Results_H6_between$def_sel, Results_H6_between$def_quant, Results_H6_between$def_mod, 
  Results_H6_between$op_def, Results_H6_between$op_op, Results_H6_between$op_sel, 
  Results_H6_between$op_quant, Results_H6_between$op_mod, Results_H6_between$sel_def, 
  Results_H6_between$sel_op, Results_H6_between$sel_sel, Results_H6_between$sel_quant, 
  Results_H6_between$sel_mod)

@@

Figure \@ref(fig:Plot46RevisedDataCode) visually illustrates the relations of QMP ratios from different QMP types between replication protocols and original articles further.

The unidimensionality of the measures used in the Many Labs projects was assessed through factor analyses, and evaluated based on the criteria discussed in the Exploratory Analyses section above. Suitable data for factor analyses was available for nineteen measures. These measures were the same as those shown in Figure \@ref(fig:Plot23AlphaCode), with the addition of one more measure from [@cacioppo1983effects]. A composite score based on the measurement responses was used for sixteen of the nineteen measures to form a single variable in the analyses, and were thus regarded as intended to be unidimensional. The number of dimensions for the remaining three were unclear. Sufficient fit of the unidimensional model was found for six out of the nineteen evaluated measures. However, as shown in Table \@ref(tab:UnidimesnionalityTestResultsTable) the unidimensional model did not hold for any measure data based on the parallel analysis test alone. Only the RMSEA $< .08$ criteria suggested evidence for single factor structures.
